Extracting sunbeams from cucumbers: Computational reproducibility is essential for archaeological science

### 2025-02-15 README.Rmd
update dockerfile

@@

## How to run in your browser or download and run locally

@@

>>>>

[![.github/workflows/knit-in-docker.yml](https://github.com/benmarwick/web-of-science-archaeology/actions/workflows/knit-in-docker.yml/badge.svg)](https://github.com/benmarwick/web-of-science-archaeology/actions/workflows/knit-in-docker.yml)

@@

## How to download and run locally

@@

## How to download and run locally in a Docker container

This research compendium includes a [Dockerfile](Dockerfile) that specifies the computational environment used to generate the results presented in the paper. You can recreate this environment on your computer by following these steps:

1. Download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip) and unzip    
2. Install [Docker](https://www.docker.com/get-started/)    
3. Open the compendium in the terminal and run `docker build -t wos .` to build the container on your computer, it will take a few minutes and require an internet connection.
4. Run in your terminal `docker run --rm -it -e ROOT=TRUE -e PASSWORD=rstudio -dp 8787:8787 wos` to run the container
5. Go to http://localhost:8787/ with your browser and enter  rstudio in both fields to start RStudio in the browser, running in the Docker container
6. In RStudio, open the project and the Quarto document, and render it
